\documentclass[a4paper,11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{multicol}

\begin{document}

\title{Resume}
\author{Biswajeet Padhi}
\date{\today}
\maketitle

\noindent
\textbf{Address:} RAYAGADA, ODISHA, PIN 765001 \\
\textbf{Phone:} +91-9777223392 \\
\textbf{Email:} biswajeetpadhi100@gmail.com \\
\textbf{LinkedIn:} www.linkedin.com/in/biswajeetpadhi \\
\textbf{GitHub:} www.github.com/biswajeetpadhi

\section*{Summary}
Passionate professional with 4.5 years of experience in the Mechanical domain, seeking a career transition into the IT industry. Seeking to enhance Python development, Machine Learning, and Deep Learning skills to deliver profitable results while leveraging prior expertise.

\section*{Work Experience}
\begin{itemize}[leftmargin=*,label=--]
  \item \textbf{iNeuron Intelligence Pvt Ltd} \\
  \textbf{Data Science Intern} (September 2022 – December 2022, BANGALORE, KARNATAKA)
  \begin{itemize}[label={$\bullet$}]
    \item Generated a Word Cloud on the independent variable.
    \item Performed data pre-processing steps like Tokenization, Stemming, Lemmatization, Part-of-speech tagging.
    \item Built a pipeline \& used the feature extraction step like TfidfVectorizer on the independent variable.
    \item Built a Multinomial Naive Bayes Model for Text Classification.
  \end{itemize}
  
  \item \textbf{iNeuron Intelligence Pvt Ltd} \\
  \textbf{Data Science Intern} (October 2022 – December 2022, BANGALORE, KARNATAKA)
  \begin{itemize}[label={$\bullet$}]
    \item Data ingestion was performed from DataStax Astra DB which is a serverless, multi-cloud database built on Apache Cassandra.
    \item Performed data visualization to generate better hypothesis.
    \item Predicted the Remaining Useful Life of the Turbofan Jet Engines in Non-Parametric modeling using RandomForestRegressor.
    \item Deployed model using FastAPI which uses modern ASGI server.
  \end{itemize}

  \item \textbf{Innodatatics} \\
  \textbf{Data Science Intern} (March 2022 – June 2022, HYDERABAD, TELANGANA)
  \begin{itemize}[label={$\bullet$}]
    \item Performed outlier treatment and data pre-processing on data.
    \item Performed OneHotEncoding to convert Categorical to binary.
    \item Predicted employee performance in non-Parametric modeling using K-NeighborsClassifier \& BaggingClassifier.
  \end{itemize}

  \item \textbf{Mythri Infrastructure and Mining India Pvt Ltd.} \\
  \textbf{Maintenance Engineer} (MARCH 2019 - DECEMBER 2020, KORAPUT, ODISHA)
  \begin{itemize}[label={$\bullet$}]
    \item Constructed \& edited the Breakdown Analysis, Monthly Cost analysis, Internal Hire Rates, Monthly Availability \& Utilization Reports Capex list, Statutory list, Of Crushing plant, Batching plant, Asphalt Plant and Heavy Construction Equipment like Excavator, Loader, Motor Grader, Soil compactor, Tipper, Transit mixer, Diesel Generator etc.
    \item Planned \& prioritized Preventive \& Periodic Maintenance of 60+ Heavy machinery equipment’s which improved the vehicles productivity by 20\%.
    \item Organized \& supervised the erection \& commissioning of all-new capex purchased \& negotiated with spare parts vendors.
  \end{itemize}

  \item \textbf{KMC Construction Ltd.} \\
  \textbf{Junior Engineer} (FEBRUARY 2016 - OCTOBER 2018, HYDERABAD, TELANGANA)
  \begin{itemize}[label={$\bullet$}]
    \item Documented \& drafted the Purchase Orders \& Indents in ERP system for mechanical parts, such as wear \& tear parts, consumable parts, serviceable parts, breakdown parts, measuring instruments and gauges, lube oils etc.
    \item Accomplished the execution and installation of all safety devices like operator fatigue system, proximity sensor, rear vision camera, auto dipping system, automatic fire detection and suppression system, load indicators in all equipment’s.
  \end{itemize}
\end{itemize}

\section*{Education}
\textbf{Mechanical Engineering} (Bachelor of Technology) \\
Gandhi Engineering College, BHUBANESWAR, ODISHA \\
AUGUST 2011 - MAY 2015

\section*{Course Certificates}
\begin{itemize}
  \item Machine Learning with Python by IBM (March 2021)
  \item Data Science using Python \& R Programming by 360DigiTMG (December 2022)
  \item Artificial Intelligence \& Deep Learning by 360DigiTMG (March 2022)
\end{itemize}

\section*{Technical Skills}
\begin{itemize}
  \item Programming Language: Python, SQL
  \item Database: MySQL, MongoDB
  \item IDE: PyCharm, Jupyter
  \item Libraries: Pandas, NumPy, Seaborn, Matplotlib, Scikit-learn, NLTK, Keras, TensorFlow, PyMySQL, PyMongo, Pipenv, Pydantic, FastAPI, Beautiful Soup
  \item Others: Statistics, Git, HTML, Jinja2, Linux Shell, Windows PowerShell, Microsoft Excel
\end{itemize}

\section*{Coursework Activities}
Data Structures \& Algorithms, Problem Solving, Data Mining, Data Manipulation, Data Wrangling, Data Processing, Hypothesis Generation, Statistical Analysis, Dimensionality Reduction, Cluster Analysis, Regression Analysis, Predictive Modelling, Statistical Modeling, Neural Networks, Hyperparameter Tuning, Web Scraping, Text mining, Model Deployment

\section*{Language Skills}
English, Hindi

\section*{Achievement}
260+ Solved problems at LeetCode

\end{document}
